---
title: "Development of Iridescence due to Exposure to Estrogen"
author: "Coley Tosto"
date: "`r Sys.Date()`"
output: html_document
---

```{r knitsetup, include=FALSE}
knitr::opts_knit$set(root.dir='../',fig_path="../figs/")
```


```{r chunksetup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,out.extra='',fig.pos="H",
                      fig.path = "../figs/",
                      dpi = 300,dev='png')
```

```{r library, message=FALSE, warning=FALSE}
library(car)
library(knitr)
library(kableExtra)
library(tidyverse)
library(ggplot2)
library(magick)
library(cowplot)
```

```{r read-data}
estrogen_data <- read.csv("processed_data/estrogen.csv")
estrogen_data$Exposure <- as.factor(estrogen_data$Exposure)

mvfiri <- read.csv("processed_data/mvfiri.csv")
```

For this analysis we are trying to see if there is a significant increase in the amount of iridescence on male pipefish after exposure to synthetic estrogen.

### Exploring Morphemetrics {.tabset}
Here we are testing to ensure that the sizes of the males used in the control versus the estrogen-exposed groups did not significantly differ in size. A difference in size may skew the way that males are affected by synthetic estrogen.

#### Summary Table
```{r table_morph, echo=FALSE}
estrogen_data %>% 
  group_by(Exposure) %>% 
  summarise(across(c("length", "depth_before", "depth_after", "SVL"),  list(mean = mean, SD = sd))) %>%
  kable(caption = "Summarized data of morphometrics including the mean and SD for each variable", format = "html",
        col.names = c("Exposure", "Length", "SD", "Depth Before", "SD", "Depth After", "SD", "SVL", "SD")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left")
```
#### Length (mm)
```{r histogram_length, message=F, echo = F, fig.cap = "Histogram of the lengths of the male pipefish in mm"}
ggplot(data = estrogen_data, aes(x = length)) +
  geom_histogram(aes(fill = Exposure), 
                 alpha = 0.5, 
                 position = "identity") +
  scale_fill_manual(values = c("darkorange","purple")) +
  theme_minimal() +
  labs(x = "Length (mm)",
       y = "# of pipefish",
       title = "Length of Male Pipefish")

```
#### Depth before Exposure (mm)
```{r histogram_dbefore, message=F, echo = F, fig.cap = "Histogram of the depths of the pipefish prior to the experiment starting"}
ggplot(data = estrogen_data, aes(x = depth_before)) +
  geom_histogram(aes(fill = Exposure), 
                 alpha = 0.5, 
                 position = "identity") +
  scale_fill_manual(values = c("darkorange","purple")) +
  theme_minimal() +
  labs(x = "Depth (mm)",
       y = "# of pipefish",
       title = "Depth of Male Pipefish DAY 1")

```
#### Depth after Exposure (mm)
```{r histogram_dafter, message=F, echo = F, fig.cap = "Histogram of the depths of the pipefish at the end of the 18 days"}
ggplot(data = estrogen_data, aes(x = depth_after)) +
  geom_histogram(aes(fill = Exposure), 
                 alpha = 0.5, 
                 position = "identity") +
  scale_fill_manual(values = c("darkorange","purple")) +
  theme_minimal() +
  labs(x = "Depth (mm)",
       y = "# of pipefish",
       title = "Depth of Male Pipefish DAY 18")

```
#### Snout-vent Length (mm)
```{r histogram_SVL, message=F, echo = F, fig.cap = "Histogram of the snout-vent length of the male piepfish"}
ggplot(data = estrogen_data, aes(x = SVL)) +
  geom_histogram(aes(fill = Exposure), 
                 alpha = 0.5, 
                 position = "identity") +
  scale_fill_manual(values = c("darkorange","purple")) +
  theme_minimal() +
  labs(x = "Snout-vent Length (mm)",
       y = "# of pipefish",
       title = "SVL of Male Pipefish")

```
### {-}
#### Analysis
```{r analysis_morph}
##Length
leveneTest(length~Exposure, estrogen_data)
t.test(length~Exposure, data = estrogen_data) #No sig. difference

##Depth day 1
leveneTest(depth_before~Exposure, estrogen_data)
t.test(depth_before~Exposure, data = estrogen_data) #No sig. difference

##Depth day 18
leveneTest(depth_after~Exposure, estrogen_data)
t.test(depth_after~Exposure, estrogen_data) #Sig. difference

##SVL
leveneTest(SVL~Exposure, estrogen_data)
t.test(SVL~Exposure, estrogen_data) #No sig. difference
```
No significant difference in the sizes of the males (including length, depth, and SVL) in the control group versus the exposure group when they entered the experiment. However, after the 18-day period males that were exposed to estrogen became significantly deeper than males in the control group. 


### Data Exploration {.tabset}
#### Summary Table
```{r table, echo=FALSE}
estrogen_data %>% 
  group_by(Exposure) %>% 
  summarise(across(c("change_iri"),  list(mean = mean, SD = sd))) %>%
  kable(caption = "Summarized Data", format = "html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "left")
```

#### Histogram
```{r histogram, message=F, echo = F, fig.cap = "Histogram of change in iridescence in males exposed vs unexposed to estrogen after 18 days"}
est_hist <- ggplot(data = estrogen_data, aes(x = change_iri)) +
  geom_histogram(aes(fill = Exposure), 
                 alpha = 0.5, 
                 position = "identity") +
  scale_fill_manual(values = c("darkorange","purple")) +
  theme_minimal() +
  labs(x = "Change in Iridescence",
       y = "Frequency",
       title = "Change in Male Iridescence Levels")
est_hist
```
### Analysis
```{r analysis}
leveneTest(change_iri~Exposure, estrogen_data)

wilcox.test(change_iri~Exposure, data = estrogen_data)
```
Signifcant different between how much iridescence was developed over the 18 day period between males that were exposed to synthetic estrogen, and those that were not exposed. Now we want to see how the level of iridescence found on males that were exposed to estrogen compared to iridescence present on females from the same location.

```{r mvfiri}
wilcox.test(Iridescence~Sex, data = mvfiri)
boxplot(Iridescence~Sex, data = mvfiri,
        ylab = "Iridescence", xlab = "Sex")
```
There is a significatn difference between the two as females do possess more iridescence. However, many of the iridescence vales for the exposed males (`r min((mvfiri[which(mvfiri$Sex == 'Male'),])$Iridescence)` - `r max((mvfiri[which(mvfiri$Sex == 'Male'),])$Iridescence)`) fall within the range of iridescence (`r min((mvfiri[which(mvfiri$Sex == 'Female'),])$Iridescence)` - `r max((mvfiri[which(mvfiri$Sex == 'Female'),])$Iridescence)`) found on wild caught females.

### Create Figure
```{r fig6, echo=F,fig.height=8, warning=F}
##Creating dataframe compatible with geom_bar
Control<-estrogen_data[which(estrogen_data$Exposure=='Control'),]
Estrogen<-estrogen_data[which(estrogen_data$Exposure=='Estrogen'),]
est <- data.frame(Exposure=c("Control","Estrogen"),
                  Changeiniri=c(mean(Control$change_iri),mean(Estrogen$change_iri)),
                  Se=c((sd(Control$change_iri)/(sqrt(5))),(sd(Estrogen$change_iri)/(sqrt(8)))))

##Making the plot
plot <- ggplot(est, aes(x=Exposure, y=Changeiniri)) + 
  geom_bar(stat = "identity",
           width=0.4,
           color="black",
           size=0.7,
           fill=c("gray77","gray37")) + 
  theme_minimal() + 
  labs(x="Exposure Level", y="Change in Iridescence") + 
  geom_errorbar(aes(x=Exposure, ymin=Changeiniri-Se, ymax=Changeiniri+Se),
                width=0.1,
                size=0.7) + 
  theme(text=element_text(size=12, family="sans", color="black")) +
  geom_hline(yintercept=0, linetype='solid', show.legend = TRUE)

##Reading in the images I want next to my plot
male_before <- ggdraw() +
               draw_image("malepipe_before.png")
male_after <- ggdraw() +
              draw_image("malepipe_after.png")

##Putting it all together
pipefish_images <- plot_grid(male_before, male_after,
                     ncol = 1,
                     byrow = TRUE,
                     labels = c('B', 'C'),
                     label_fontfamily = 'sans',
                     label_fontface = 'bold',
                     label_size = 18,
                     rel_widths = c(1, 1))
barplot <- plot_grid(plot,
                     ncol = 1,
                     labels = c('A'),
                     label_fontfamily = 'sans',
                     label_fontface = 'bold',
                     label_size = 18)
plot_grid(barplot, pipefish_images, NULL, NULL,
          ncol = 2,
          byrow = TRUE,
          scale = c(1, 0.9))

```